2024 US Presidential Election Model

### 2024-10-20 paper/paper.qmd
committing rendered file

## Model

Define \( y_i \) as the binary outcome variable indicating whether Donald Trump is predicted to win state \( i \) (1 if Trump wins, 0 if Harris wins). The predictor variables are \( \beta_i \), the average percentage of polling support for Donald Trump in state \( i \), and \( \gamma_i \), the average percentage of polling support for Kamala Harris in state \( i \).

\[
y_i|\mu_i, \sigma \sim \mbox{Bernoulli}(\mu_i)
\]
\[
\mu_i = \alpha + \beta_i + \gamma_i
\]
\[
\alpha \sim \mbox{Normal}(0, 2.5)
\]
\[
\beta_i \sim \mbox{Normal}(0, 2.5)
\]
\[
\gamma_i \sim \mbox{Normal}(0, 2.5)
\]

@@

### Model Justification

@@

### Predicted Election Winner By State
```{r}
#| label: fig-statemap
#| fig-cap: Predicted Election Winner by State
#| echo: false
#| warning: false
#| message: false
#| cache: false

@@

# Check that state_average has the correct number of rows and no grouping
print(nrow(state_average))  # Ensure this number matches the expected rows

>>>>

## Model
Define \( y_i \) as the binary outcome variable indicating whether Donald Trump is predicted to win state \( i \) (1 if Trump wins, 0 if Harris wins). The predictor variables are \( \beta_i \), the average percentage of polling support for Donald Trump in state \( i \), and \( \gamma_i \), the average percentage of polling support for Kamala Harris in state \( i \).

\[
y_i|\mu_i \sim \text{Bernoulli}(\mu_i)
\]
\[
\mu_i = \alpha + \beta_i + \gamma_i
\]
\[
\alpha \sim \text{Normal}(0, 2.5)
\]
\[
\beta_i \sim \text{Normal}(0, 2.5)
\]
\[
\gamma_i \sim \text{Normal}(0, 2.5)
\]

@@

## Model Justification

@@

## Predicted Election Winner By State
```{r}
#| label: fig-statemap
#| fig-cap: Predicted Election Winner by State
#| echo: false
#| warning: false
#| message: false
#| cache: false

@@
